What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-03-01 icpc/icpc2010.tex
intro para 1 what's in a name

Unlike the poetic licence Shakespeare uses, we show that names are indeed important. In this paper we `name' and label topic models generated by a topic modeling technique, Latent Dirichlet Allocation~\cite{Blei2003}. We use these topic models to train supervised learners to classify larger datasets. We also show that these topics can be generalized across products.

>>>>

Unlike the poetic license Shakespeare uses, we show that names are indeed important. The rose has its own tangible properties which allow us to sense it. Unfortunately when we are dealing with data abstracted from program source code, we are already dealing with abstract entities that are not tangible.

In this paper we `name' and label topic models generated by a topic modeling technique, Latent Dirichlet Allocation~\cite{Blei2003}. We use these topic models to train supervised learners to classify larger datasets. We also show that these topics can be generalized across products.
